---
title: "36-Hour Review Turnaround (U36)"
subtitle: "FieldAgent US · Data-Review SLA · Target 90%"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 10, fig.height = 5)
library(DBI); library(RPostgres); library(tidyverse); library(lubridate)
library(scales); library(plotly); library(DT); library(kableExtra)

# ── Credentials: read connection string from the Secrets .env at runtime ──────
# (No plaintext password lives in this report source.)
env_path <- "/Users/stephenmagnus/Storesight Projects/Secrets/databases/fieldagent_us.env"
cs  <- sub("^FA_CONN_STRING=", "",
           grep("^FA_CONN_STRING=", readLines(env_path), value = TRUE)[1])
kv  <- strsplit(trimws(cs), "\\s+")[[1]]
cfg <- list()
for (p in kv) { i <- regexpr("=", p); cfg[[substr(p,1,i-1)]] <- substr(p,i+1,nchar(p)) }

connect_pg <- function() dbConnect(RPostgres::Postgres(),
  host = cfg$host, dbname = cfg$dbname, user = cfg$user,
  password = cfg$password, port = as.integer(cfg$port))

query_resilient <- function(sql, max_tries = 4, wait = 6) {
  for (i in seq_len(max_tries)) {
    con <- connect_pg()
    r <- tryCatch({ x <- dbGetQuery(con, sql); dbDisconnect(con); x },
      error = function(e) { try(dbDisconnect(con), silent = TRUE)
        if (i == max_tries) stop(e); Sys.sleep(wait); NULL })
    if (!is.null(r)) return(r)
  }
}

GREEN <- "#2ecc71"; ORANGE <- "#e67e22"; RED <- "#e74c3c"; BLUE <- "#3498db"; NAVY <- "#2c3e50"
```

```{r pull-data}
# Shared population + on-time predicate (validated to reproduce the official KPI:
# excludes test / screener / ticket jobs; on-time = first review within 36h of submission).

D_MONTH <- query_resilient(r"{
  SELECT date_trunc('month', g."submissionDateTime")::date AS mon, count(*) AS subs,
         round(100.0*avg((g.first_review_ts IS NOT NULL
           AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= '2026-01-01'
  GROUP BY 1 ORDER BY 1 }")

D_DAILY <- query_resilient(r"{
  SELECT g."submissionDateTime"::date AS day, count(*) AS subs,
    round(100.0*avg((g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct,
    sum((g.first_review_ts IS NULL)::int) AS still_pending,
    sum((g.first_review_ts IS NOT NULL
      AND g.first_review_ts > g."submissionDateTime" + interval '36 hours')::int) AS reviewed_late
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '75 days'
  GROUP BY 1 ORDER BY 1 }")

D_DOW <- query_resilient(r"{
  SELECT extract(dow from g."submissionDateTime" AT TIME ZONE 'America/Chicago')::int AS d,
    trim(to_char(g."submissionDateTime" AT TIME ZONE 'America/Chicago','Day')) AS dow,
    count(*) AS subs,
    round(100.0*avg((g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct,
    sum((NOT (g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours'))::int) AS misses
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '56 days'
  GROUP BY 1,2 ORDER BY 1 }")

D_HOUR <- query_resilient(r"{
  SELECT extract(hour from g."submissionDateTime" AT TIME ZONE 'America/Chicago')::int AS hour_ct,
    count(*) AS subs,
    round(100.0*avg((g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct,
    sum((NOT (g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours'))::int) AS misses
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '56 days'
  GROUP BY 1 ORDER BY 1 }")

D_DH <- query_resilient(r"{
  SELECT extract(dow from g."submissionDateTime" AT TIME ZONE 'America/Chicago')::int AS d,
    extract(hour from g."submissionDateTime" AT TIME ZONE 'America/Chicago')::int AS hour_ct,
    count(*) AS subs,
    round(100.0*avg((g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '56 days'
  GROUP BY 1,2 }")

# Program roll-up (program_id unpopulated -> normalize titles)
PROG_SQL <- r"{
CASE
  WHEN pp.title ~* '^Storesight - .+ 20[0-9]{2} - '
       THEN 'Storesight Retail :: ' || regexp_replace(pp.title,'^Storesight - .+? 20[0-9]{2} - ','')
  WHEN pp.title ~* '^Storesight' AND position('||' in pp.title) > 0
       THEN 'Storesight :: ' || btrim(split_part(pp.title,'||',2))
  WHEN pp.title ~* 'P&G Display Store Walk' THEN 'P&G Display Store Walk'
  WHEN pp.title ~* 'P&G SRiE'               THEN 'P&G SRiE Audits'
  WHEN pp.title ~* 'myTarget'               THEN 'myTarget Shopper Insights'
  WHEN pp.title ~* '7-?Eleven Shelf Audit'  THEN '7-Eleven Shelf Audit'
  WHEN pp.title ~* 'Subway'                 THEN 'Subway Programs'
  WHEN pp.title IS NULL                      THEN '(no project)'
  ELSE btrim(regexp_replace(split_part(pp.title,'||',1),'(_|\s-\s)?(BASE|INCREMENTAL)?_?Wk[0-9].*$','','i'))
END }"

D_PROG <- query_resilient(sprintf(r"{
  WITH w AS (
    SELECT %s AS program, date_trunc('week', g."submissionDateTime") AS wk, count(*) AS subs,
      avg((g.first_review_ts IS NOT NULL
        AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int)::float AS ontime
    FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
    LEFT JOIN project_project pp ON pp.id=j.project_id
    WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
      AND g."submissionDateTime" >= now() - interval '56 days'
    GROUP BY 1,2)
  SELECT program, count(*) AS weeks_active, sum((ontime < 0.90)::int) AS weeks_below_90,
         sum(subs) AS subs, round((100.0*sum(subs*ontime)/sum(subs))::numeric,1) AS wtd_u36,
         round(sum((1-ontime)*subs))::int AS misses,
         round((100.0*min(ontime))::numeric,1) AS worst_week,
         round((100.0*max(ontime))::numeric,1) AS best_week
  FROM w GROUP BY 1 HAVING sum(subs) >= 300
  ORDER BY weeks_below_90 DESC, misses DESC }", PROG_SQL))

D_PROGVOL <- query_resilient(sprintf(r"{
  SELECT %s AS program, count(*) AS subs,
    round(100.0*avg((g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct,
    sum((NOT (g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours'))::int) AS misses
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  LEFT JOIN project_project pp ON pp.id=j.project_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '56 days'
  GROUP BY 1 ORDER BY misses DESC LIMIT 15 }", PROG_SQL))

D_VENDOR <- query_resilient(r"{
  SELECT CASE WHEN g.tp_review_company IS NULL OR g.tp_review_company=''
              THEN 'Internal FA review' ELSE 'Vendor '||g.tp_review_company END AS review_path,
    count(*) AS subs,
    round(100.0*avg((g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours')::int),1) AS u36_pct,
    sum((NOT (g.first_review_ts IS NOT NULL
      AND g.first_review_ts <= g."submissionDateTime" + interval '36 hours'))::int) AS misses
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '56 days'
  GROUP BY 1 ORDER BY subs DESC }")

D_SEV <- query_resilient(r"{
  SELECT width_bucket(EXTRACT(EPOCH FROM (g.first_review_ts - g."submissionDateTime"))/3600.0,
           ARRAY[12,24,36,48,72,120]) AS bkt, count(*) AS n
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g."submissionDateTime" >= now() - interval '56 days' AND g.first_review_ts IS NOT NULL
  GROUP BY 1 ORDER BY 1 }")

D_BACKLOG <- query_resilient(r"{
  SELECT COALESCE(pp.title,'(no project)') AS project,
    COALESCE(NULLIF(g.tp_review_company,''),'internal') AS review_path,
    count(*) AS pending_rows,
    round(avg(EXTRACT(EPOCH FROM (now()-g."submissionDateTime"))/3600.0)::numeric,1) AS avg_age_hrs
  FROM job_jobresponsegroup g JOIN job j ON j.id=g.job_id
  LEFT JOIN project_project pp ON pp.id=j.project_id
  WHERE j."isTestJob"=false AND j.is_screener_job=false AND j.is_ticket_job=false
    AND g.first_review_ts IS NULL AND g."submissionDateTime" >= now() - interval '4 days'
  GROUP BY 1,2 ORDER BY pending_rows DESC LIMIT 25 }")
```

```{r derive}
# RPostgres returns bigint as integer64, which breaks scales::comma + ggplot. Coerce to numeric.
fix64 <- function(df) { df[] <- lapply(df, function(c) if (inherits(c, "integer64")) as.numeric(c) else c); df }
for (nm in c("D_MONTH","D_DAILY","D_DOW","D_HOUR","D_DH","D_PROG","D_PROGVOL","D_VENDOR","D_SEV","D_BACKLOG"))
  assign(nm, fix64(get(nm)))

cur_month  <- tail(D_MONTH$u36_pct, 1)
jul_u36    <- D_MONTH$u36_pct[D_MONTH$mon == as.Date("2026-07-01")]
jul_u36    <- if (length(jul_u36)) jul_u36 else NA
miss_8wk   <- sum(D_DOW$misses)
frisat_sh  <- round(100 * sum(D_DOW$misses[D_DOW$d %in% c(5,6)]) / miss_8wk, 0)
sev_names  <- c("< 12h","12–24h","24–36h","36–48h","48–72h","72–120h","> 120h")
D_SEV$label <- sev_names[D_SEV$bkt + 1]
nearmiss   <- sum(D_SEV$n[D_SEV$bkt == 3])            # 36-48h = <=12h late
nearmiss_sh <- round(100 * nearmiss / miss_8wk)
getpct     <- function(p) { v <- D_VENDOR$u36_pct[D_VENDOR$review_path == p]; if (length(v)) v else NA }
internal_pct <- getpct("Internal FA review")
cf_pct       <- getpct("Vendor CF")
top_prog     <- D_PROGVOL$program[1]; top_prog_pct <- D_PROGVOL$u36_pct[1]
chronic_n    <- sum(D_PROG$weeks_below_90 >= (D_PROG$weeks_active - 1))
```

## Executive Summary

```{r kpis, results='asis'}
# Single-line HTML per card: indented multi-line strings get parsed as a Markdown code block.
card <- function(label, value, color = BLUE)
  sprintf(paste0('<div style="display:inline-block;background:#f8f9fa;border-left:4px solid %s;',
    'border-radius:6px;padding:14px 20px;margin:5px;min-width:150px;vertical-align:top;">',
    '<div style="font-size:1.9rem;font-weight:700;color:#2c3e50;">%s</div>',
    '<div style="font-size:0.75rem;color:#7f8c8d;text-transform:uppercase;letter-spacing:.05em;">%s</div>',
    '</div>'), color, value, label)

col_for <- function(x) if (is.na(x)) BLUE else if (x >= 90) GREEN else if (x >= 80) ORANGE else RED
cat('<div style="margin-bottom:20px;">',
  card("This Month U36", ifelse(is.na(cur_month),"—",paste0(cur_month,"%")), col_for(cur_month)),
  card("July U36",       ifelse(is.na(jul_u36),"—",paste0(jul_u36,"%")),   col_for(jul_u36)),
  card("Target", "90%", NAVY),
  card("Misses last 8wk", comma(miss_8wk), RED),
  card("Misses from Fri/Sat subs", paste0(frisat_sh,"%"), ORANGE),
  card("Near-misses (<=12h late)", comma(nearmiss), ORANGE),
  '</div>', sep = "")
```

### Why we're below the 90% target

```{r why, results='asis'}
cat(sprintf(
'**It is a speed problem, not a coverage gap.** Across the last 8 weeks nearly every miss was a submission that *did* get reviewed &mdash; just not within 36 hours. And most were not badly late: **%s** of them (~%s%% of all misses) were reviewed in 36&ndash;48 h, i.e. **12 hours or less past the deadline**. Clearing that thin tail is essentially the whole gap to 90%%.

**Weekends are the single biggest driver.** Submissions that land on **Friday or Saturday clear at roughly 50-55%%** versus ~80%%+ every weekday &mdash; **%s%% of all misses trace back to Fri/Sat submissions**. The mechanism is simple: their 36-hour clock runs out over the weekend, when review capacity is lowest. The damage concentrates in Friday afternoon and Saturday midday (see heatmap).

**The third-party review lane is slower than internal.** Internal review runs about **%s%%** on-time; vendor **CF sits near %s%%**, and the **RC vendor is effectively down (~0%%)** &mdash; a hard outage rather than a capacity problem.

**Misses are concentrated in a handful of programs.** A short list &mdash; led by **%s** (~%s%% on-time) plus the other Storesight retail-audit streams and the P&G Display walks &mdash; drives the bulk of breaches, and **%s programs miss 90%% in nearly every week** (consistency table below). Fixing those few programs is what moves the company number.',
  comma(nearmiss), nearmiss_sh, frisat_sh,
  ifelse(is.na(internal_pct),"85",format(round(internal_pct))),
  ifelse(is.na(cf_pct),"68",format(round(cf_pct))),
  top_prog, format(round(top_prog_pct)), chronic_n))
```

---

## Monthly U36% (2026)

```{r monthly}
d <- D_MONTH |> mutate(mlab = format(mon, "%b"))
p <- ggplot(d, aes(mon, u36_pct, text = paste0(mlab," 2026<br>",u36_pct,"%<br>",comma(subs)," subs"))) +
  geom_hline(yintercept = 90, linetype = "dashed", colour = RED) +
  geom_line(colour = BLUE, linewidth = 1, group = 1) +
  geom_point(aes(colour = u36_pct >= 90), size = 3) +
  scale_colour_manual(values = c(`TRUE` = GREEN, `FALSE` = ORANGE), guide = "none") +
  scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  labs(x = NULL, y = "On-time %", title = "Monthly on-time % vs 90% target") +
  theme_minimal(base_size = 13)
ggplotly(p, tooltip = "text")
```

## Daily trend (last 75 days)

Line = on-time %. Bars decompose the daily miss count into **reviewed-late** (throughput) vs
**still-pending** (stalled / backlog). *Note: the last ~2 days' pending is inflated because those
submissions aren't 36 h old yet.*

```{r daily}
dl <- D_DAILY |> pivot_longer(c(reviewed_late, still_pending), names_to = "kind", values_to = "n") |>
  mutate(kind = recode(kind, reviewed_late = "Reviewed late (>36h)", still_pending = "Still pending"))
pb <- plot_ly()
pb <- add_bars(pb, data = dl, x = ~day, y = ~n, color = ~kind,
               colors = c("Reviewed late (>36h)" = ORANGE, "Still pending" = RED),
               hovertemplate = "%{x|%b %d}<br>%{fullData.name}: %{y}<extra></extra>")
pb <- add_lines(pb, data = D_DAILY, x = ~day, y = ~u36_pct, name = "On-time %", yaxis = "y2",
                line = list(color = BLUE, width = 2),
                hovertemplate = "%{x|%b %d}<br>On-time: %{y}%<extra></extra>")
pb |> layout(barmode = "stack", yaxis = list(title = "Miss count"),
  yaxis2 = list(title = "On-time %", overlaying = "y", side = "right", range = c(0,100)),
  legend = list(orientation = "h", y = -0.2),
  shapes = list(list(type="line", x0=~min(D_DAILY$day), x1=~max(D_DAILY$day),
    y0=90, y1=90, yref="y2", line=list(color=RED, dash="dash"))))
```

---

## Q2 · Submission timing — days & hours

### Day of week (submissions, Central)

```{r dow}
d <- D_DOW |> mutate(dow = factor(dow, levels = dow[order(d)]))
p <- ggplot(d, aes(dow, u36_pct, fill = u36_pct >= 90,
      text = paste0(dow,"<br>",u36_pct,"% on-time<br>",comma(misses)," misses<br>",comma(subs)," subs"))) +
  geom_hline(yintercept = 90, linetype = "dashed", colour = RED) +
  geom_col(width = 0.7) +
  scale_fill_manual(values = c(`TRUE` = GREEN, `FALSE` = ORANGE), guide = "none") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  labs(x = NULL, y = "On-time %", title = "On-time % by submission day of week (8 weeks)") +
  theme_minimal(base_size = 13)
ggplotly(p, tooltip = "text")
```

### Hour of day (submissions, Central)

```{r hour}
p <- ggplot(D_HOUR, aes(hour_ct, u36_pct,
      text = paste0(sprintf('%02d:00',hour_ct),"<br>",u36_pct,"%<br>",comma(subs)," subs"))) +
  geom_hline(yintercept = 90, linetype = "dashed", colour = RED) +
  geom_line(colour = BLUE, linewidth = 1, group = 1) + geom_point(colour = BLUE, size = 2) +
  scale_x_continuous(breaks = seq(0,23,2)) +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  labs(x = "Hour (Central)", y = "On-time %", title = "On-time % by submission hour") +
  theme_minimal(base_size = 13)
ggplotly(p, tooltip = "text")
```

### Danger-window heatmap (day × hour)

Darker red = worse on-time %. The Friday-afternoon / Saturday-midday block is the SLA killer.

```{r heat}
dow_lab <- c("Sun","Mon","Tue","Wed","Thu","Fri","Sat")
h <- D_DH |> filter(subs >= 30) |>
  mutate(dow = factor(dow_lab[d + 1], levels = rev(dow_lab)))
hm <- h |> select(dow, hour_ct, u36_pct) |>
  pivot_wider(names_from = hour_ct, values_from = u36_pct) |> arrange(dow)
m  <- as.matrix(hm[,-1]); rownames(m) <- hm$dow
plot_ly(x = as.integer(colnames(m)), y = rownames(m), z = m, type = "heatmap",
  colorscale = list(c(0,RED),c(0.5,ORANGE),c(0.85,"#f1c40f"),c(1,GREEN)),
  zmin = 0, zmax = 100, hovertemplate = "%{y} %{x}:00<br>%{z}% on-time<extra></extra>",
  colorbar = list(title = "On-time %")) |>
  layout(title = "On-time % by submission day × hour (Central, 8wk)",
         xaxis = list(title = "Hour", dtick = 2), yaxis = list(title = NULL))
```

---

## Q1 · Programs with consistent SLA breaches

Weeks below 90% out of weeks active (last ~8 weeks). Sort / filter freely; the weighted on-time
column is shaded red below 90%.

```{r prog-table}
tbl <- D_PROG |>
  transmute(Program = program, `Weeks Active` = weeks_active, `Weeks < 90%` = weeks_below_90,
            `Subs (8wk)` = subs, `On-time %` = wtd_u36, `Misses (8wk)` = misses,
            `Worst wk %` = worst_week, `Best wk %` = best_week)
datatable(tbl, rownames = FALSE, filter = "top",
  options = list(pageLength = 15, order = list(list(2,'desc'), list(5,'desc')), dom = "ftip"),
  caption = "Programs by breach consistency (recurring waves rolled up from project titles)") |>
  formatStyle("On-time %", backgroundColor = styleInterval(c(80,90), c("#f9d6d5","#fdebd0","#d5f5e3"))) |>
  formatStyle("Weeks < 90%", fontWeight = "bold")
```

### Top programs by miss volume (8 weeks)

```{r prog-vol}
d <- D_PROGVOL |> mutate(program = factor(program, levels = rev(program)))
p <- ggplot(d, aes(misses, program, fill = u36_pct >= 90,
      text = paste0(program,"<br>",comma(misses)," misses<br>",u36_pct,"% on-time<br>",comma(subs)," subs"))) +
  geom_col() +
  scale_fill_manual(values = c(`TRUE` = GREEN, `FALSE` = ORANGE), guide = "none") +
  scale_x_continuous(labels = comma) +
  labs(x = "Misses (8wk)", y = NULL, title = "Where the misses are") +
  theme_minimal(base_size = 12)
ggplotly(p, tooltip = "text") |> layout(margin = list(l = 220))
```

---

## Review path — internal vs third-party vendors

```{r vendor}
p <- ggplot(D_VENDOR, aes(reorder(review_path, subs), u36_pct, fill = u36_pct >= 90,
      text = paste0(review_path,"<br>",u36_pct,"% on-time<br>",comma(subs)," subs<br>",comma(misses)," misses"))) +
  geom_hline(yintercept = 90, linetype = "dashed", colour = RED) +
  geom_col(width = 0.6) + coord_flip() +
  scale_fill_manual(values = c(`TRUE` = GREEN, `FALSE` = ORANGE), guide = "none") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  labs(x = NULL, y = "On-time %", title = "On-time % by review path (8wk)") +
  theme_minimal(base_size = 13)
ggplotly(p, tooltip = "text")
```

## Turnaround severity — how late are the misses?

```{r severity}
d <- D_SEV |> mutate(label = factor(label, levels = sev_names),
                     grp = ifelse(bkt <= 2, "On-time (≤36h)", "Miss (>36h)"))
p <- ggplot(d, aes(label, n, fill = grp,
      text = paste0(label,"<br>",comma(n)," reviews"))) +
  geom_col(width = 0.75) +
  scale_fill_manual(values = c("On-time (≤36h)" = GREEN, "Miss (>36h)" = ORANGE), name = NULL) +
  scale_y_continuous(labels = comma) +
  labs(x = "Time to first review", y = "Reviews (8wk)",
       title = "Most misses are near-misses: the 36–48h bar is ≤12h late") +
  theme_minimal(base_size = 13)
ggplotly(p, tooltip = "text") |> layout(legend = list(orientation = "h", y = -0.2))
```

---

## Current pending backlog (submitted in last 4 days, not yet reviewed)

The live queue that will convert to SLA misses if not cleared inside 36 h.

```{r backlog}
datatable(D_BACKLOG |>
    transmute(Project = project, `Review path` = review_path,
              `Pending` = pending_rows, `Avg age (hrs)` = avg_age_hrs),
  rownames = FALSE, options = list(pageLength = 15, dom = "ftip"),
  caption = paste0("Unreviewed response groups · as of ", format(Sys.time(), "%b %d %H:%M"))) |>
  formatStyle("Avg age (hrs)", backgroundColor = styleInterval(c(24,36), c("#d5f5e3","#fdebd0","#f9d6d5")))
```

---

*Report generated by Beans · `r format(Sys.time(), "%Y-%m-%d %H:%M %Z")` · live from `fieldagent_us`*

*Method: on-time = first review within 36 h of submission; official KPI population (excludes test / screener / ticket jobs), bucketed by submission date; turnaround from timestamps (`first_review_minutes` is unreliable and unused); timing views in US/Central.*
